\addcontentsline{toc}{chapter}{Abstract}

\begin{center} {\bf Abstract} \end{center}

%write a brief abstract about you and and about this course (what knowledge can you get from this course)
In this Project  we focus on management in a large project using Latex.In large projects, such as reports, keeping parts of your document in several .tex files makes the task of correcting errors and making further changes easier. It's simpler to locate a specific word or element in a short file. For this purpose this report was created as an example of  managing big projects. \newline

In large LATEX documents one usually has several .tex files, one for each chapter or section, and then they are joined together to generate a single output. This helps to keep everything organized and makes easier to debug the document, but as the document gets larger the compilation takes longer. This can be frustrating since one is usually only interested in working in a particular file each time. \newline

You can find labs folder with laboratory works that were done during course.Those are samples of what has been studied and used hereinafter.Such as math,tables,multi-columns, references packages used correspondingly,implemented in chapters within report. \newline

 Me as a student get to know LATEX basics and its possibilities as edit tool in organization of scientific and research work.That was good pre-diploma  practice and I consider using LATEX over Word.My most favourite part in this tool is 
 mathematics formulas edit.


\clearpage 
